A Domain Specific Language for Functional Code Fusion for Intrusion Detection Algorithms in Wireless Sensor Networks

### 2014-09-22 paper.tex
more minor changes
more abstract touch-ups + preliminary structure

\title{A Domain Specific Language for Functional Code Fusion of
       Intrusion Detection Algorithms in Wireless Sensor Networks}

@@

Introducing intrusion detection in a wireless sensor network puts a strain on
the limited resources of its nodes. Fusing the underlying algorithms' code can
alleviate this, but the manual and repetitive labor proves to an unacceptable
economic burden. Intrusion detection algorithms share common functionality and
therefore are a prime candidate for applying a domain specific language. In
this paper we propose such a domain specific language to describe these
algorithms in a formal and functional way. This allows for the automation of
the fusion of these algorithms on a functional level though code generation.
The code, produced by a prototype code generator, shows to have less impact on
e.g. the execution time of the resulting intrusion detection system and its use
of the wireless network.

@@

\bibliographystyle{IEEEtran}
\bibliography{referenties}

>>>>

\title{A Domain Specific Language for Functional Code Fusion for
       Intrusion Detection Algorithms in Wireless Sensor Networks}

@@

Introducing intrusion detection in wireless sensor network (WSNs) puts a strain
on the limited resources of its nodes. Fusion of the underlying algorithms can
alleviate this, but the manual and repetitive labor proves to be an
unacceptable economic burden and is error-prone. Intrusion detection algorithms
share common functionality and structure, and therefore are a prime candidate
for the application of a domain specific language (DSL). In this paper we
propose such a DSL to describe these algorithms in a formal and functional way.
This allows for the automation of the fusion of these algorithms on a
functional level though code generation. The code, produced by a prototype code
generator implementation, shows to have less impact on e.g. the execution time
of the resulting intrusion detection system and its use of the wireless
network, in comparison with a basic side-by-side implementation of the same
algorithms.

@@

\section{Introduction}

WSN

IDS as a non-functional cost

Economics of development

Functional Code Fusion

The remainder of this paper proceeds as follows: ...

\section{Related Work}

DSL for WSN

DSL for IDS

Code Generation for WSN

Code Optimization for embedded systems/WSN

Code Generation for IDS

\section{Background}

Theory of Loop Fusion

Examples of code/loop fusion (e.g. Haskell Stream Fusion)

Function Inlining (e.g. TinyOS)

\section{Problem Analysis}

\section{Evaluation}

network usages: number of packets, number of bytes

processing time

image size

TODO: memory usage

2 algorithms
TODO: adding 3rd ?

\section{Conclusions and Future Work}

theoretical gains are met in practice

\section*{Acknowledgements}

We would like to thank the reviewers for their thoughtful and helpful comments
that enhanced the readability of this paper. Our gratitude and respect also
goes out to all members of the NES task force at KU Leuven/DistriNet for
creating the nurturing environment where these ideas could grow.

% \bibliographystyle{IEEEtran}
% \bibliography{referenties}
